Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-26 paper/galsize_paper.tex
Reworded first sentence of abstract

\begin{abstract}
Using new measurements of the projected two-point correlation function, $\wproj(\rproj)$, of  the Sloan Digital Sky Survey galaxies of different sizes and stellar masses,
 we place empirical constraints on the connection between galaxy size and halo virial radius.  
We find that small galaxies cluster much more strongly than large galaxies of the same stellar mass. 
The magnitude of this clustering difference increases on small scales, and decreases with increasing stellar mass. 
Using {\tt Halotools} to forward model the observations, we test a simple empirical model in which present-day galaxy size is 
proportional to the size of the virial radius at the time the halo reached its maximum mass. This simple model reproduces the 
observed size-dependence of $\wproj(\rproj)$ in striking detail. 
The success of this model provides strong support for the conclusion that satellite galaxies have smaller sizes relative to central 
galaxies of the same halo mass. 
Our findings indicate that satellite size is set prior to the time of infall, and that a remarkably simple, linear size--virial radius relation 
emerges from the complex physics regulating galaxy size. 
We make quantitative predictions for future measurements of galaxy-galaxy lensing, including dependence upon size, scale, 
and stellar mass, and provide a simple scaling relation of the ratio of mean sizes of satellites and central galaxies as a function of their halo mass 
that can be used to calibrate hydrodynamical simulations and semi-analytic models. 
\end{abstract}

>>>>

\begin{abstract}
Using new measurements of $\wproj(\rproj)$, the projected two-point correlation function of galaxies of different sizes and stellar masses observed in the Sloan Digital Sky Survey, we place empirical constraints on the connection between galaxy size and halo virial radius.  
We find that small galaxies cluster much more strongly than large galaxies of the same stellar mass. 
The magnitude of this clustering difference increases on small scales, and decreases with increasing stellar mass. 
Using {\tt Halotools} to forward model the observations, we test a simple empirical model in which present-day galaxy size is 
proportional to the size of the virial radius at the time the halo reached its maximum mass. This simple model reproduces the 
observed size-dependence of $\wproj(\rproj)$ in striking detail. 
The success of this model provides strong support for the conclusion that satellite galaxies have smaller sizes relative to central 
galaxies of the same halo mass. 
Our findings indicate that satellite size is set prior to the time of infall, and that a remarkably simple, linear size--virial radius relation 
emerges from the complex physics regulating galaxy size. 
We make quantitative predictions for future measurements of galaxy-galaxy lensing, including dependence upon size, scale, 
and stellar mass, and provide a simple scaling relation of the ratio of mean sizes of satellites and central galaxies as a function of their halo mass 
that can be used to calibrate hydrodynamical simulations and semi-analytic models. 
\end{abstract}
